|

### 2020-04-05 paper.tex
Edits to appendix.
Added link to PLOS One example.

  \begin{itemize}
  \tightlist
  \item
    Use adobe acrobat (commerical software) to convert your file to a word file. Then open in word and delete all the parts that shouldn't go into the word count. The word count is displayed in the lower right.
  \item
    Use an one of the online services to count your words (search for ``pdf word count'')
  \end{itemize}
\end{itemize}

@@

>>>>

  \begin{itemize}
  \tightlist
  \item
    Use adobe acrobat (commerical software) to convert your file to a word file. Then open in word and delete all the parts that shouldn't go into the word count. The word count is displayed in the lower right.
  \item
    Use an one of the online services to count your words (search for ``pdf word count'')
  \end{itemize}
\item
  Appendix: You can change the numbering format for the appendix in the rmd file

  \begin{itemize}
  \tightlist
  \item
    What is still not possible in this document is to automatically have separate reference sections for paper and appendix.
  \end{itemize}
\item
  Journals may require you to use their tex style: Sometimes you can simply use their template in your rmarkdown file. See \href{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/LDUMNY}{here} for a PLOS one example.
\end{itemize}

@@

\clearpage
\pagenumbering{arabic}

\hypertarget{online-appendix}{%
\section{Online appendix}\label{online-appendix}}
